Characterizing Stellar Streams by ML

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

    The result of applying our density model to the synthetic data is
    illustrated in \autoref{fig:mock_data_result}. The top panel shows the
    weight parameter that controls membership probability as a function of
    $\phi_1$. The dashed curve represents the output of our data-driven model,
    while the solid curve is the ground truth. The second panel shows the stream
    and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the
    stream and background in the $(\phi_1,\parallax)$ plane. Points are
    color-coded according to their membership probability
    \autoref{eq:membership_prob}. The weight parameter clearly shows that the
    model has captured the two prominent density variations along the stream.
    The are additional variations  mostly around the edges of the stream, though
    re-sampling the neural network weights with dropout reveals that these
    variations represent regions of higher model uncertainty.

>>>>

    The result of applying our density model to the synthetic data is
    illustrated in \autoref{fig:mock_data_result}. The top panel shows the
    weight parameter that controls membership probability as a function of
    $\phi_1$. The dashed curve represents the output of our data-driven model,
    while the solid curve is the ground truth. The second panel shows the stream
    and background in the $(\phi_1,\phi_2)$ plane, and the third panel shows the
    stream and background in the $(\phi_1,\parallax)$ plane. Points are
    color-coded according to their membership probability
    \autoref{eq:membership_prob}. The weight parameter clearly shows that the
    model has captured the two prominent density variations along the stream.
    There are additional variations, mostly around the edges of the stream, though
    re-sampling the neural network weights with dropout reveals that these
    variations represent regions of higher model uncertainty.
